Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-12 cosmic_voids.tex
seccion 3 revisada

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  Fractional Anisotropy field over a slide of the simulation for each
  web scheme (T-Web is up. V-Web is down).  
  Middle column. Cosmic Web identification. Voids
  are white, sheets are light gray, filaments are dark gray and
  knots are black.
  Right column. Colors are voids identified by our Fractional
  Anisotropy method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The left panel shows the correlation between $\lambda_1$ and $FA$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the local overdensity $\delta$.  
This shows that the overdensity has a large scatter at fixed
$\lambda_1$.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-web and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

@@

The previous section shows that FA is a good void tracer, but it does
not automatically suggest how to define the boundary of individual
voids.
For this purpose, we
use the \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} to identify a void as the basin of FA
local minimum. 
The advantage of this definition is that we can
now forget about the free parameter $\lambda_{th}$. 
Additionally, this algorithm does not require any assumption on the
shape and/or morphology of the tentative voids.

The watershed technique has been already implemented to find voids \citet{Platen07,
Neyrinck08} however it used the density field instead of the FA
field as we suggest in this paper. 
Another difference with respect to other void finding implementations
is that we estimate all relevant quantities on a Cartesian mesh of fixed cell
size, while it other works use an adaptive Delaunay tessellation
\citep{Schaap00}. 
However from the analysis of our results this different does not seem
to introduce supurious results, at least with the mass resolution we
have in the N-body simulation.

This watershed algorithm still needs a threshold value to reduce
spurious features and to avoid void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
two voids with overdensity below that value is removed to merge the
respective voids. 
In our case we have to find a corresponding FA value
to define this threshold.

@@

The right column in Figure \ref{fig:FA_field} shows all the voids that
have been identified using the watershed algorithm on the FA field.

>>>>

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  Fractional Anisotropy field over a slide of the simulation for each
  web scheme (T-Web top. V-Web bottom).  
  Middle column. Cosmic Web identification. Voids
  are white, sheets are light gray, filaments are dark gray and
  knots are black.
  Right column. Colors are voids identified by our Fractional
  Anisotropy method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The right panel shows the correlation between $\lambda_1$ and $\delta$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the FA. This shows that the
overdensity has a large scatter at fixed $\lambda_1$.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-web and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells FA$<0.95$.   
The middle panels in Figure \ref{fig:FA_field} show the web
classification for this choice of $\lambda_{th}$, demonstrating that
this FA level is a sensitive choice to define voids.

@@

The previous section shows that FA is a good void tracer, but it does
not automatically suggest how to define the boundary of individual
voids.
For this purpose, we use the \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} to identify a void as the basin of FA
local minimum. 
The advantage of this definition is that it does not require any
assumption on the shape and/or morphology of the tentative voids.

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the the density field
instead of the FA field as we do in this paper
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
However, from the analysis of our results it does not 
introduce supurious results, at least with the mass resolution we have
in the N-body simulation.

The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
two voids with overdensity below that value is removed to merge the
respective voids. 
In our case we have to find a corresponding FA value
to define this threshold.

@@

The right column in Figure \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field. 
In what follows we describe the numerical simulation we have used to
find voids and their detailed properties characterization.
